---
title: "Advertisement Detection"
author: "Kiran Kumar Patro"
date: "September 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading libraries

```{r}

library(stringr)
library(outliers)
library(zoo)
library(ISLR)
library(caret)
library(caTools)
library(ggplot2)
library(lattice)
```

#Clearing environment variables
#Setting work directory

```{r}

rm(list = ls(all=TRUE))
setwd("C:/Users/welcome/Downloads/internship")

```



#Loading dataset

```{r}

x=file.choose(new = FALSE)
add_data<-read.csv(x, header = TRUE)
add_data$X<-NULL
str(add_data, list.len=ncol(add_data))
```

#Summary of the dataset

```{r}

options(max.print=999999)
summary(add_data)


```


#Replacing '?' with NA's

```{r}

add_data$X0=as.character(add_data$X0)
add_data$X0=as.numeric(add_data$X0)
add_data$X3<- as.numeric(add_data$X3)

add_data$X1=as.character(add_data$X1)
add_data$X1=as.numeric(add_data$X1)

add_data$X2=as.character(add_data$X2)
add_data$X2=as.numeric(add_data$X2)


```



#Detecting outliers and Replacing them with NA in Height, Width and Aspect Ratio attributes

```{r}
add_data$X0 <- with(add_data, ifelse(is.na(X0)==TRUE,NA,ifelse(X0<30, NA,ifelse(X0>600,NA,X0))))
add_data$X1 <- with(add_data, ifelse(is.na(X1)==TRUE,NA,ifelse(X1<88, NA,ifelse(X1>728,NA,X1))))
add_data$X2 <- with(add_data, ifelse(is.na(X2)==TRUE,NA,ifelse(X2<0.14, NA,ifelse(X2>24.26,NA,X2))))
```

#Building a function to calculate Mode
#This function is built in such a way that it works for data types of numeric,character and factor
#This function ignores NA's and calculates Mode for rest of the values in the data

```{r}
Mode <- function(x) {
  ux <- na.omit(unique(x) )
  ux[which.max(tabulate(match(x, ux)))]
}

```


#Replacing the NA's in Height, width, Aspect Ratio and local variables by Mode of Height, Width, Aspect Ratio and local respectively

```{r}
for(i in 1:length(add_data$X0))
{
  if(is.na(add_data$X0[i])==TRUE)
  {
    add_data$X0[i]=Mode(x=add_data$X0)
  }
}

for(i in 1:length(add_data$X1))
{
  if(is.na(add_data$X1[i])==TRUE)
  {
    add_data$X1[i]=Mode(x=add_data$X1)
  }
}

for(i in 1:length(add_data$X2))
{
  if(is.na(add_data$X2[i])==TRUE)
  {
    add_data$X2[i]=Mode(x=add_data$X2)
  }
}


```

# Data Pre-processing

## Train/Test Split

* Split the data 70/30 into train and test sets, by setting the seed as "112"

```{r}

set.seed(112)

train_rows <- createDataPartition(add_data$X1558,p=0.7,list = F)

train_data <- add_data[train_rows, ]


test_data <- add_data[-train_rows, ]

```


```{r}

library(caret)

preprocessmodel=preProcess(add_data[,!names(add_data) %in% c("X1558 ")],method=c("center","scale"))
train_data[,!names(train_data)%in% c("X1558 ")]=predict(object = preprocessmodel,newdata=train_data[,!names(train_data) %in% c("X1558 ")])
test_data[,!names(train_data)%in% c("X1558 ")]=predict(object = preprocessmodel,newdata=test_data[,!names(train_data) %in% c("X1558 ")])



```

#Apply PCA on the Original Data
*Project the train and test data sets onto the derived principal components

```{r}
pca <- prcomp(train_data[, !(names(train_data) %in% c("X1558"))])
train_datanew<-predict(pca,train_data)
train_datanew<-data.frame(train_data)

plot(pca, type = "l")
summary(pca)
train_datared<-data.frame(subset(train_datanew,select=c(X1:X162)))
test_datared<-data.frame(subset(test_data,select=c(X1:X162)))
str(train_datared)

```


```{r}
y<-train_data$X1558
train_datanew1<-as.data.frame(cbind(train_datared,y))
y<-test_data$X1558
test_datanew1<-cbind(test_datared,y)
```



